The Two Dualities of Computation: Negative and Fractional Types

### 2012-03-08 rational.tex
_

The reductions for the primitive isomorphisms are exactly the same as
have been persented before \cite{infeffects}. The reductions for the
closure combinators are however presented in a small-setp operational
style. The following are the definition for evaluation contexts and
machine states:

@@

The reduction rules below essentially track the flow of particles
through their circuit. The start machine state, {{<c,v,[]>}}, denotes
the particle/value {{v}} about to be evluated by the circuit
{{c}}. The end machine state, {{[c, v, [] ]}}, denotes the situation
where the particle {{v}} has exited the circuit {{c}}.

@@

Rules (5) to (9) deal with {{c1 (+) c2}} in the same way. In the case
of sums, the shape of the value {{left v}}/{{right v}} determines
whether path {{c1}} or path {{c2}} is taken. Rules (10), (11) and (12)
deal with {{c1 (*) c2}} similarly. In the case of products the value
should have the form {{(v1, v2)}} where {{v1}} flows through {{c1}}
and {{v2}} flows through {{c2}}. Both these paths are entirely
independant of each other and we could chosen to evaluate either
first, or evaluate both in parallel. In this presentation we have
chosen to follow {{c1}] first, but this choice is entirely artificial.

Finally, we end by noting the abstract machine here is interesting is
that it is a reversible machine. We could change reductions `{{|-->}}'
to run backwards `{{<--|}}', thereby computing the start state from the
stop state. We will take advantange of this property in
Sec. \ref{sec:rat}.

@@

\roshan{We really have to rethink this prop in the precense of
  negatives and fractionals. With negatives, the program can actually
  end at the begining of the circuit -- i.e. the program {{c:b1<->b2}}
  can stop with a value of type {{b1}}. With fractionals, there can be
  several values of type {{b2}} produced for a value of type {{b1}}. }

@@

\roshan{I chose to draw the igure with b instead of a, since b is what
  we use for the types. Should this be a? Also I chose to make the
  swap and 0 wires, explicit.Is this what you intended? }

>>>>

The reductions for the primitive isomorphisms are exactly the same as
have been presented before \cite{infeffects}. The reductions for the
closure combinators are however presented in a small-step operational
style. The following are the definition for evaluation contexts and
machine states:

@@

The reduction rules below essentially track the flow of particles
through their circuit. The start machine state, {{<c,v,[]>}}, denotes
the particle/value {{v}} about to be evaluated by the circuit
{{c}}. The end machine state, {{[c, v, [] ]}}, denotes the situation
where the particle {{v}} has exited the circuit {{c}}.

@@

Rules (5) to (9) deal with {{c1 (+) c2}} in the same way. In the case
of sums, the shape of the value {{left v}}/{{right v}} determines
whether path {{c1}} or path {{c2}} is taken. Rules (10), (11) and (12)
deal with {{c1 (*) c2}} similarly. In the case of products the value
should have the form {{(v1, v2)}} where {{v1}} flows through {{c1}}
and {{v2}} flows through {{c2}}. Both these paths are entirely
independent of each other and we could chosen to evaluate either
first, or evaluate both in parallel. In this presentation we have
chosen to follow {{c1}] first, but this choice is entirely artificial.

Finally, we end by noting the abstract machine here is interesting is
that it is a reversible machine. We could change reductions `{{|-->}}'
to run backwards `{{<--|}}', thereby computing the start state from
the stop state. We will take advantage of this property in
Sec. \ref{sec:rat}.

@@

\roshan{We really have to rethink this prop in the presence of
  negatives and fractionals. With negatives, the program can actually
  end at the beginning of the circuit -- i.e. the program {{c:b1<->b2}}
  can stop with a value of type {{b1}}. With fractionals, there can be
  several values of type {{b2}} produced for a value of type {{b1}}. }

@@

\roshan{I chose to draw the figure with b instead of a, since b is what
  we use for the types. Should this be a? Also I chose to make the
  swap and 0 wires, explicit.Is this what you intended? }
